Vragenlijst thesis evaluatie

### 2015-06-08 doc/template/chap-5.tex
beetje overal verbeteren

Another addition of Laszka et al. to the game of FlipIt \cite{MitigationCovert} 
is extending the game to also consider non-targeted attacks by non-strategic players. In this game the defender tries to maintain control over the resource that is subjected to both targeted and non-targeted attacks. Non-targeted attacks can include phishing, while targeted attacks may include threats delivered through zero day attack vulnerabilities. \\
One of the last important additions from Laszka et al. \cite{MitigationNonTargeted} is to consider a game where the moves made by the attacker are still covert but the moves made by the defender are known to the attacker. This means that the attacker can base his attacks on the defender's moves. Both the targeted and non-targeted attacks do not succeed immediately. For the targeted attack the time till it succeeds is given by an exponential distributed random variable with a known rate. The non-targeted attacks are modelled as a single attacker and the time till it succeeds is given by a Poisson process. The conclusion of this paper is that the optimal strategy for the defender is moving periodically. The difference with this paper is that the delay in this paper is dependent on the number of nodes that have to be flipped in a network. This cannot be modelled with the framework in the Laszka et al. paper because the delay is chosen as an exponential distributed random variable. Another difference is that in the case of the Laszka et al. paper, the moves of the defender are considered not stealthy and so the attacker knows when the defender plays. \\

Other authors used the FlipIt game to apply it on a specific scenario. To be able to use the FlipIt game, modifications where required for the FlipIt model.
One of the scenarios by Pham \cite{compromised} was to find out whether a resource was compromised or not by the attacker. This could be verified by the defender, who has an extra move "test" beside the flip move. The basic idea is to test with an extra action if the resource has been compromised or not. This move involves also an extra cost.\\

Finally researchers also have investigated the behaviour of humans playing FlipIt. A. Nochenson and Grossklags \cite{nochenson2013behavioral}  investigate how people really act when given temporal decisions. Reitter et al. \cite{reitter2013risk} extended the work of A. Nochenson and Grossklags to include various visual presentation modalities for the available feedback during the investigation.

>>>>

Another addition of Laszka et al. to the game of FlipIt \cite{MitigationCovert} 
is extending the game to also consider non-targeted attacks by non-strategic players. In this game the defender tries to maintain control over the resource that is subjected to both targeted and non-targeted attacks. Non-targeted attacks can include phishing, while targeted attacks may include threats delivered through zero day attack vulnerabilities. \\
One of the last important additions from Laszka et al. \cite{MitigationNonTargeted} is to consider a game with targeted and non-targeted attacks where the moves made by the attacker do not succeed immediately. This is similar to this paper but it has still some major differences. First the moves by the attacker are still covert but the moves made by the defender are known to the attacker. This means that the attacker knows when the defender plays and can change its strategy depending on the moves of the defender. Our motivation for a defender with stealthy moves is that there is not always an intelligent individual that is behind an APT. Some APTs don't know if the computer is already been recovered. There purpose is to spread. Not to check if they have already infected. \todo{beter verwoorden}. The second difference is that even though both the targeted and non-targeted attacks do not succeed immediately, the delay is determined differently. For the targeted attack the time till it succeeds is given by an exponential distributed random variable with a known rate. The non-targeted attacks are modelled as a single attacker and the time till it succeeds is given by a Poisson process. In our paper the delay is given by one parameter, that can be the result of any virus propagation model. The third and last difference is that the paper of Laska has multiple attackers and they try to find the best strategy of the defender against both targeted and non-targeted attacks. The conclusion of this paper is that the optimal strategy for the defender is moving periodically. \\

FlipIt has also been applied to several cases in system security. Reseachers explored different applications of FlipIt for real-world problems, like password reset policies, VM refresh, cloud auditing and key rotation \cite{ApplyingFlipit}. \\
Other authors used the FlipIt game to apply it on a specific scenario. To be able to use the FlipIt game, modifications where required for the FlipIt model.
One of the scenarios by Pham \cite{compromised} was to find out whether a resource was compromised or not by the attacker. This could be verified by the defender, who has an extra move "test" beside the flip move. The basic idea is to test with an extra action if the resource has been compromised or not. This move involves also an extra cost.\\
A three-player game has also been investigated where the flipit framework of two players is extended by another player. This player represents an insider that trades value information with the attacker \cite{fengstealthy}.\\

Finally researchers also have investigated the behaviour of humans playing FlipIt. A. Nochenson and Grossklags \cite{nochenson2013behavioral}  investigate how people really act when given temporal decisions. They found out that the results improves over time but that they are dependent on gender, age, and other individual difference variables. The result also shows that the participants perform generally better when they have more information about the strategy of the opponent which is a computerized player. Reitter et al. \cite{reitter2013risk} extended the work of A. Nochenson and Grossklags to include various visual presentation modalities for the available feedback during the investigation.\\

### 2015-06-08 doc/template/chap-9.tex
beetje overal verbeteren

\section{Introduction}
\label{Ch2:Intro}

\section{FlipIt game with virus propagation}

Motivatie voor het veranderen van FLipIt naar een FlipIt met viruspropagatie:

\section{Explaining difference between FlipIt with and without virus propagation}

A FlipIt game consists of a single resource. To represent the security problem, the game now defines its single resource as a computer network with multiple
nodes. One of the players, the defender, will try to defend his network. The defender
will do this by flipping all the nodes of the network (i.e. the entire resource) in every move he plays. The
attacker, the other player, will try to infect all the nodes in the network. The attacker
will do this by flipping the node in the graph that can infect all the nodes in the
shortest possible time. After dropping a virus on the first node, it takes a while for the virus to infect the entire network. Since the original FlipIt game works with a single resource that is always flipped entirely, the assumption is made that the attacker is considered to gain immediate full control over the resource when the network has been infected, even it is only one node that has been infected.\\

@@

\section{Formal definition Game}

In this section we provide a formal definition of the game and the notation that we will use throughout the paper.

\begin{description}
\item $i$: Defines the player. Different as in the FlipIt paper where the defender is denoted by the subscript 0 and the attacker by the subscript 1.
\item $\delta_{i}$: The length of the interval between two consecutive moves of player \textit{i}. 
\item $\alpha_{i}$: The average flip rate of player \textit{i}, given by $\alpha_{i}=1/\alpha_{i}$.
\item $k_{i}$: The cost of player \textit{i}'s moves.
\item $d$: The delay caused by the virus propagation.
\item $G_{i}(t)$: The total gain of player \textit{i} denotes the amount of time player \textit{i} is in control over the resource up to time \textit{t}.
\item $\gamma_{i}$: The average gain rate of player \textit{i} defined as $G_{i}(t)/t$
\item $\beta_{i}$:  The average benefit rate up to time \textit{t} defined as  $\beta_{i} = \gamma_{i} -k_{i} \alpha_{i} $.
\item $opt_{i}$: The optimum function.
\end{description}

\todo{tekening toevoegen waarop de delay staat aangeduid}

\section*{Playing periodically with virus propagation}

This chapter explains how to model a FlipIt game with a virus propagation that infects a network. The first section explains the difference between a normal FlipIt game and a FlipIt game with virus propagation. The next section derives a formula to calculate the benefit for a FlipIt game with a virus propagation. In the last section we calculate the Nash equilibrium for the benefit formula.

@@

\subsection{Formalization the benefit formula including the infection-delay}
 A Periodic strategy is a non-adaptive renewal strategy where the time intervals between consecutive moves are a fixed period, denoted by $\delta$. Moreover it has a random phase, that is chosen uniformly and random in the interval $[0,\delta]$ for the first move. The average rate of play of a player is denoted by $\alpha_{i} = \dfrac{1}{\delta_{i}}$. \\
~~\\

@@

\begin{equation}
\beta_{A}(\alpha_{D},\alpha_{A}) =\dfrac {r} {2} - k_{A} \alpha_{A} = \dfrac {\delta_{D}} {2\delta_{A}} - k_{A} \alpha_{A}  
\end{equation}\\

Correspondingly, the benefit for the defender can be expressed as:
\begin{equation}
\beta_{D}(\alpha_{D},\alpha_{A}) =1 -  \dfrac {r} {2} - k_{D} \alpha_{D} = 1 - \dfrac {\delta_{D}} {2\delta_{A}} - k_{D} \alpha_{D} 
\end{equation}

\begin{figure}[hbtp]
\caption{The first FlipIt game is one without virus propagation. The second one is with virus propagation and \textit{d} = 1. The delay is denoted with an arrow.}
\centering
\includegraphics[scale=0.4]{../../doc/template/Images/FLipItCase1.pdf}
\label{fig:delaycase1}
\end{figure}

However, because of the delay required for virus propagation, the maximal time of control is reduced to $\delta_{D}-d$ , see figure \ref{fig:delaycase1}. There is a probability of \textit{r} that the attacker will move in the interval of the defender. However, the gain will not be half of the interval. Indeed, the attacker has to play soon enough to gain control, meaning that the attacker has to play during the period of $\delta_{D}-d$ during the interval of the defender. The probability that the attacker plays soon enough is $\dfrac{\delta_{D}-d}{\delta_{D}}$ and this will give the attacker an average gain of $\dfrac{\delta_{D}-d}{2}$. If the attacker moves after the period of $\delta_{D}-d$, the gain of the attacker will be zero. The probability that this happens is  $\dfrac{d}{\delta_{D}}$. The average gain rate of the attacker can then be expressed as follows if we look at one interval of the defender:
\begin{equation}
\gamma_{A}(\alpha_{D},\alpha_{A}) = \dfrac {1}{\delta_{D}} [ \dfrac{\delta_{D}}{\delta_{A}} \cdot \dfrac{\delta_{D}-d}{\delta_{D}} \cdot \dfrac{\delta_{D}-d}{2} + \dfrac{\delta_{D}}{\delta_{A}} \cdot \dfrac{d}{\delta_{D}} \cdot 0 ]
\end{equation}

To derive the benefit, the cost of moving is subtracted from the average gain. 
\begin{equation}
\beta_{A}(\alpha_{D},\alpha_{A}) = \dfrac { (\delta_{D}-d) ^{2}} {2 \cdot \delta_{D}  \delta_{A}} - k_{A} \alpha_{A}
\end{equation}
\begin{equation}
\beta_{A}(\alpha_{D},\alpha_{A}) = \dfrac { \delta_{D}} {2 \cdot \delta_{A}} - k_{A} \alpha_{A} - ( \dfrac{d^{2}}{2 \cdot \delta_{A} \delta_{D}} - \dfrac{d}{\delta_{A}} )
\end{equation}

 The benefit of the defender is expressed as follows:
\begin{equation}
\beta_{D}(\alpha_{D},\alpha_{A}) = 1 - \dfrac { (\delta_{D}-d) ^{2}} {2 \cdot \delta_{D}  \delta_{A}} - k_{D} \alpha_{D}
\end{equation}
~~\\
We can easily see that when $d$=0, we obtain the formula of the original FlipIt game.\\

@@

\begin{equation}
\beta_{D}(\alpha_{D},\alpha_{A}) = \dfrac {1} {2r} - k_{D} \alpha_{D} = \dfrac {\delta_{A}} {2\delta_{D}} - k_{D} \alpha_{D} 
\end{equation}
\begin{equation}
\beta_{A}(\alpha_{D},\alpha_{A}) =1 - \dfrac {1} {2r} - k_{A} \alpha_{A} = 1- \dfrac {\delta_{A}} {2\delta_{D}} - k_{A} \alpha_{A}  
\end{equation}\\

An intuitive solution for the case with a virus would be to subtract the benefit of the attacker received in each interval with the delay similarly as in case 1. This would give us the following formula if we derive it in the same way:
\begin{equation}
\beta_{A}=\dfrac{(\delta_{A} - d)^2}{2\delta_{A}\delta_{D}} - \dfrac{k_{A}}{\delta_{A}}
\end{equation}

@@

\begin{equation}\label{first}
\gamma_{D}(\alpha_{D},\alpha_{A}) = \dfrac{\delta_{A}}{\delta_{D}} \cdot \dfrac{(d+\dfrac{\delta_{A}}{2})}{\delta_{A}} 
\end{equation}
\begin{equation}\label{first}
\gamma_{D}(\alpha_{D},\alpha_{A}) = \dfrac{\delta_{A}}{2\delta_{D}} + \dfrac{d}{\delta_{D}} 
\end{equation}\\
This yields in the following benefit formula:
\begin{equation}\label{first}
\beta_{D}(\alpha_{D},\alpha_{A}) = \dfrac{\delta_{A}}{2\delta_{D}} + \dfrac{d}{\delta_{D}} - k_{D} \alpha_{D} 
\end{equation}\\

The benefit for the attacker will be as follows:
\begin{equation}\label{first}
\beta_{A}(\alpha_{D},\alpha_{A}) = 1 -\dfrac{\delta_{A}}{2\delta_{D}} - \dfrac{d}{\delta_{D}} - k_{A} \alpha_{A} 
\end{equation}\\

@@

\begin{equation}\label{first}
\dfrac{1} {\delta_{A}} \cdot \dfrac{d - (\delta_{D} - \delta_{A})}{\delta_{D}} \cdot \dfrac{d - (\delta_{D} - \delta_{A})}{\delta_{D}}
\end{equation}

The total gain  rate of the defender is obtained by subtracting this term from the gain rate of case a:
 \begin{equation}\label{first}
\gamma_{D}(\alpha_{D},\alpha_{A}) = \dfrac{\delta_{A}}{\delta_{D}} \cdot \dfrac{(d+\dfrac{\delta_{A}}{2})}{\delta_{A}} - \dfrac{(d - (\delta_{D} - \delta_{A}))^{2}}{2 \delta_{D} \delta_{A}}
\end{equation}
\begin{equation}\label{first}
\gamma_{D}(\alpha_{D},\alpha_{A}) = \dfrac{\delta_{A}}{2\delta_{D}} + \dfrac{d}{\delta_{D}} - \dfrac{(d - (\delta_{D} - \delta_{A}))^{2}}{2 \delta_{D} \delta_{A}}
\end{equation}\\
This yields in the following benefit formula:
\begin{equation}\label{first}
\beta_{D}(\alpha_{D},\alpha_{A}) = \dfrac{\delta_{A}}{2\delta_{D}} + \dfrac{d}{\delta_{D}} - k_{D} \alpha_{D} - \dfrac{(d - (\delta_{D} - \delta_{A}))^{2}}{2 \delta_{D} \delta_{A}}
\end{equation}\\

The benefit for the attacker will be as follows:
\begin{equation}\label{first}
\beta_{A}(\alpha_{D},\alpha_{A}) = 1 -\dfrac{\delta_{A}}{2\delta_{D}} - \dfrac{d}{\delta_{D}} - k_{A} \alpha_{A} + \dfrac{(d - (\delta_{D} - \delta_{A}))^{2}}{2 \delta_{D} \delta_{A}}
\end{equation}\\

>>>>

\section{Introduction}
\label{Ch2:Intro}
The game of FlipIt with virus propagation considers attackers where their moves are not instantaneous. This can be motivated by an example of a virus. A virus can be dropped on a network but it only compromises the whole network if every node in the network is infected. The basic FlipIt game does not take this into account. In this chapter the FlipIt game with virus propagation is explained and how it can be modelled. First the main differences with the basic FlipIt game are discussed in section \ref{ch2:diffFlip}. Next in section \ref{ch2:formal} the formal definition of the game with virus propagation is given. At last, in section \ref{ch2:periodicvirus} a periodic strategy game is considered and the formalization of the formulas with virus propagation are determined.\\

This chapter explains how to model a FlipIt game with a virus propagation that infects a network. The first section explains the difference between a normal FlipIt game and a FlipIt game with virus propagation. The next section derives a formula to calculate the benefit for a FlipIt game with a virus propagation. In the last section we calculate the Nash equilibrium for the benefit formula.
\section{FlipIt game with virus propagation}

Motivation

\section{Explaining difference between FlipIt with and without virus propagation}
\label{ch2:diffFlip}

A FlipIt game consists of a single resource. To represent the security problem, the game now defines its single resource as a computer network with multiple
nodes. One of the players, the defender, will try to defend his network. The defender
will do this by flipping all the nodes of the network (i.e. the entire resource) in every move he plays. The
attacker on the other hand will try to infect all the nodes in the network. The attacker
will do this by flipping the node in the graph that can infect all the nodes in the
shortest possible time. After dropping a virus on the first node, it takes a while for the virus to infect the entire network. Since the original FlipIt game works with a single resource that is always flipped entirely, the assumption is made that the attacker is considered to gain immediate full control over the resource when the network has been infected, even it is only one node that has been infected.\\

@@

\section{Playing periodically with virus propagation}
\label{ch2:periodicvirus}

@@

\subsection{Formalization the benefit formula including the infection-delay}

 A Periodic strategy is a non-adaptive renewal strategy where the time intervals between consecutive moves are a fixed period, denoted by $\delta$. Moreover it has a random phase, that is chosen uniformly and random in the interval $[0,\delta]$ for the first move. The average rate of play of a player is denoted by $\alpha_{i} = \dfrac{1}{\delta_{i}}$. List of symbols that will be used throughout the paper. Figure \ref{FlipItDelay} represents a couple of the symbols for clarification.\\
~~\\
\begin{figure}[hbtp]
\caption{Formalization of a FlipIt game with delay: A representation of a FlipIt game where both players are playing periodically. Every move or flip is indicated by a blue or orange circle.  The defender is represented in blue and plays with a period of $\delta_{D}$. The flip of the attacker is represented by a white circle, but because there is a delay d, the attacker only controls the resource after time d represented by an orange circle. The attacker plays with a period of $\delta_{A}$. The blue and orange rectangles represent the amount of time the respective player is in control of the resource.}
\centering
\includegraphics[scale=0.7]{Images/DefFlip.png}
\label{FlipItDelay}
\end{figure}

\begin{description}
\item $i$: Defines the player. Different as in the FlipIt paper where the defender is denoted by the subscript 0 and the attacker by the subscript 1.
\item $\delta_{i}$: The length of the interval between two consecutive moves of player \textit{i}. 
\item $\alpha_{i}$: The average flip rate of player \textit{i}, given by $\alpha_{i}=1/\delta_{i}$.
\item $k_{i}$: The cost of player \textit{i}'s moves.
\item $d$: The delay caused by the virus propagation.
\item $G_{i}(t)$: The total gain of player \textit{i} denotes the amount of time player \textit{i} is in control over the resource up to time \textit{t}.
\item $\gamma_{i}$: The average gain rate of player \textit{i} defined as $G_{i}(t)/t$
\item $\beta_{i}$:  The average benefit rate up to time \textit{t} defined as  $\beta_{i} = \gamma_{i} -k_{i} \alpha_{i} $.
\item $opt_{i}$: The optimum function.
\end{description}

@@

\begin{equation*}
\beta_{A}(\alpha_{D},\alpha_{A}) =\dfrac {r} {2} - k_{A} \alpha_{A} = \dfrac {\delta_{D}} {2\delta_{A}} - k_{A} \alpha_{A}  
\end{equation*}\\

Correspondingly, the benefit for the defender can be expressed as:
\begin{equation*}
\beta_{D}(\alpha_{D},\alpha_{A}) =1 -  \dfrac {r} {2} - k_{D} \alpha_{D} = 1 - \dfrac {\delta_{D}} {2\delta_{A}} - k_{D} \alpha_{D} 
\end{equation*}

\begin{figure}[hbtp]
\caption{Case 1: Difference between a basic FlipIt game and a FlipIt game with a delay. (1) is the FlipIt game without a delay and (2) is with a delay. The delay is denoted with an arrow. The attacker is only in control when the circle becomes orange.}
\centering
\includegraphics[scale=0.6]{../../doc/template/Images/DiffDelayCase1.png}
\label{fig:delaycase1}
\end{figure}

However, because of the delay required for virus propagation, the maximal time of control is reduced to $\delta_{D}-d$ , see figure \ref{fig:delaycase1}. There is a probability of \textit{r} that the attacker will move in the interval of the defender. However, the gain will not be half of the interval. Indeed, the attacker has to play soon enough to gain control, meaning that the attacker has to play during the period of $\delta_{D}-d$ during the interval of the defender. The probability that the attacker plays soon enough is $\dfrac{\delta_{D}-d}{\delta_{D}}$ and this will give the attacker an average gain of $\dfrac{\delta_{D}-d}{2}$. If the attacker moves after the period of $\delta_{D}-d$, the gain of the attacker will be zero. The probability that this happens is  $\dfrac{d}{\delta_{D}}$. The average gain rate of the attacker can then be expressed as follows if we look at one interval of the defender:
\begin{equation*}
\gamma_{A}(\alpha_{D},\alpha_{A}) = \dfrac {1}{\delta_{D}} [ \dfrac{\delta_{D}}{\delta_{A}} \cdot \dfrac{\delta_{D}-d}{\delta_{D}} \cdot \dfrac{\delta_{D}-d}{2} + \dfrac{\delta_{D}}{\delta_{A}} \cdot \dfrac{d}{\delta_{D}} \cdot 0 ]
\end{equation*}

To derive the benefit, the cost of moving is subtracted from the average gain. 
\begin{equation*}
\beta_{A}(\alpha_{D},\alpha_{A}) = \dfrac { (\delta_{D}-d) ^{2}} {2 \cdot \delta_{D}  \delta_{A}} - k_{A} \alpha_{A}
\end{equation*}
\begin{equation*}
\beta_{A}(\alpha_{D},\alpha_{A}) = \dfrac { \delta_{D}} {2 \cdot \delta_{A}} - k_{A} \alpha_{A} - ( \dfrac{d^{2}}{2 \cdot \delta_{A} \delta_{D}} - \dfrac{d}{\delta_{A}} )
\end{equation*}

 The benefit of the defender is expressed as follows:
\begin{equation*}
\beta_{D}(\alpha_{D},\alpha_{A}) = 1 - \dfrac { (\delta_{D}-d) ^{2}} {2 \cdot \delta_{D}  \delta_{A}} - k_{D} \alpha_{D}
\end{equation*}
~~\\
We can easily see that when $d$=0, we obtain the formula of the original FlipIt game.\\

@@

\begin{equation*}
\beta_{D}(\alpha_{D},\alpha_{A}) = \dfrac {1} {2r} - k_{D} \alpha_{D} = \dfrac {\delta_{A}} {2\delta_{D}} - k_{D} \alpha_{D} 
\end{equation*}
\begin{equation*}
\beta_{A}(\alpha_{D},\alpha_{A}) =1 - \dfrac {1} {2r} - k_{A} \alpha_{A} = 1- \dfrac {\delta_{A}} {2\delta_{D}} - k_{A} \alpha_{A}  
\end{equation*}\\

An intuitive solution for the case with a virus would be to subtract the benefit of the attacker received in each interval with the delay similarly as in case 1. This would give us the following formula if we derive it in the same way:
\begin{equation*}
\beta_{A}=\dfrac{(\delta_{A} - d)^2}{2\delta_{A}\delta_{D}} - \dfrac{k_{A}}{\delta_{A}}
\end{equation*}

@@

\begin{equation*}\label{first}
\gamma_{D}(\alpha_{D},\alpha_{A}) = \dfrac{\delta_{A}}{\delta_{D}} \cdot \dfrac{(d+\dfrac{\delta_{A}}{2})}{\delta_{A}} 
\end{equation*}
\begin{equation*}\label{first}
\gamma_{D}(\alpha_{D},\alpha_{A}) = \dfrac{\delta_{A}}{2\delta_{D}} + \dfrac{d}{\delta_{D}} 
\end{equation*}\\
This yields in the following benefit formula:
\begin{equation*}\label{first}
\beta_{D}(\alpha_{D},\alpha_{A}) = \dfrac{\delta_{A}}{2\delta_{D}} + \dfrac{d}{\delta_{D}} - k_{D} \alpha_{D} 
\end{equation*}\\

The benefit for the attacker will be as follows:
\begin{equation*}\label{first}
\beta_{A}(\alpha_{D},\alpha_{A}) = 1 -\dfrac{\delta_{A}}{2\delta_{D}} - \dfrac{d}{\delta_{D}} - k_{A} \alpha_{A} 
\end{equation*}\\

@@

\begin{equation*}
\dfrac{1} {\delta_{A}} \cdot \dfrac{d - (\delta_{D} - \delta_{A})}{\delta_{D}} \cdot \dfrac{d - (\delta_{D} - \delta_{A})}{\delta_{D}}
\end{equation*}

The total gain  rate of the defender is obtained by subtracting this term from the gain rate of case a:
 \begin{equation*}
\gamma_{D}(\alpha_{D},\alpha_{A}) = \dfrac{\delta_{A}}{\delta_{D}} \cdot \dfrac{(d+\dfrac{\delta_{A}}{2})}{\delta_{A}} - \dfrac{(d - (\delta_{D} - \delta_{A}))^{2}}{2 \delta_{D} \delta_{A}}
\end{equation*}
\begin{equation*}
\gamma_{D}(\alpha_{D},\alpha_{A}) = \dfrac{\delta_{A}}{2\delta_{D}} + \dfrac{d}{\delta_{D}} - \dfrac{(d - (\delta_{D} - \delta_{A}))^{2}}{2 \delta_{D} \delta_{A}}
\end{equation*}\\
This yields in the following benefit formula:
\begin{equation*}
\beta_{D}(\alpha_{D},\alpha_{A}) = \dfrac{\delta_{A}}{2\delta_{D}} + \dfrac{d}{\delta_{D}} - k_{D} \alpha_{D} - \dfrac{(d - (\delta_{D} - \delta_{A}))^{2}}{2 \delta_{D} \delta_{A}}
\end{equation*}\\

The benefit for the attacker will be as follows:
\begin{equation*}
\beta_{A}(\alpha_{D},\alpha_{A}) = 1 -\dfrac{\delta_{A}}{2\delta_{D}} - \dfrac{d}{\delta_{D}} - k_{A} \alpha_{A} + \dfrac{(d - (\delta_{D} - \delta_{A}))^{2}}{2 \delta_{D} \delta_{A}}
\end{equation*}\\

### 2015-06-08 doc/template/nash.tex
beetje overal verbeteren

\textbf{Case: $\delta_{D} \leq \delta_{A} $\\

@@

\begin{equation}
 \beta_{D}(\alpha_{D},\alpha_{A})}{\partial \alpha_{D}} = \dfrac{\delta_{A}}{2\delta_{D}} + \dfrac{d}{\delta_{D}} - \dfrac{k_{D}}{\delta_{D}}
\end{equation}
\begin{equation}
\frac{\partial \beta_{D}(\alpha_{D},\alpha_{A})}{\partial \alpha_{D}} = -\dfrac{\delta_{A}}{2\delta_{D}^{2}} - \dfrac{d}{\delta_{D}^{2}} + \dfrac{k_{D}}{\delta_{D}^{2}}
\end{equation}

@@

\begin{equation}
\beta_{D}(\alpha_{D},\alpha_{A})}{\partial \alpha_{D}} = \dfrac{\delta_{A}}{2\delta_{D}} + \dfrac{d}{\delta_{D}} - \dfrac{k_{D}}{\delta_{D}} - \dfrac{(d-(\delta_{D} - \delta_{A}))^{2}}{d\delta_{D}\delta_{A}}
\end{equation}

@@

%%% Local Variables: 
%%% mode: latex
%%% TeX-master: "thesis"
%%% End:

>>>>

\textbf{Case: $\delta_{D} \leq \delta_{A} $}\\

@@

\begin{equation}
\dfrac{t \beta_{D}(\alpha_{D},\alpha_{A})}{\partial \alpha_{D}} = \dfrac{\delta_{A}}{2\delta_{D}} + \dfrac{d}{\delta_{D}} - \dfrac{k_{D}}{\delta_{D}}
\end{equation}
\begin{equation}
\frac{\partial \beta_{D}(\alpha_{D},\alpha_{A})}{\partial \alpha_{D}} = -\dfrac{\delta_{A}}{2\delta_{D}^{2}} - \dfrac{d}{\delta_{D}^{2}} + \dfrac{k_{D}}{\delta_{D}^{2}}
\end{equation}

@@

\begin{equation}
\dfrac{\beta_{D}(\alpha_{D},\alpha_{A})}{\partial \alpha_{D}} = \dfrac{\delta_{A}}{2\delta_{D}} + \dfrac{d}{\delta_{D}} - \dfrac{k_{D}}{\delta_{D}} - \dfrac{(d-(\delta_{D} - \delta_{A}))^{2}}{d\delta_{D}\delta_{A}}
\end{equation}

@@

The optimum functions will be piecewise functions. There will be different optimum functions depending on $k_{D}$ and $d$. Two cases are considered.
\subsubsection{$k_{D} \leq d$}

\begin{description}
\item if $\delta_{A} < 2(k_{D} - d)$ \\
For case 2.A it is decreasing. Because $k_{D} \leq d$ the term $2(k_{D} - d)$ will always be negative so $\delta_{A}$ will also be negative. This means for case 1 and case 2.b that $\delta_{D} = 0$ and so the defender will not play.
\item $\delta_{A} = 2(k_{D} - d)$ \\
$\delta_{A} = 0$ so the attacker will not play. For case 1 and case 2.b the defender will also not play.
\item $\delta_{A} > 2(k_{D} - d)$ \\
For case 2.b it is decreasing. Case 2.a it is increasing. For case 1 $2(k_{D} - d)$ is always negative so the minimum is 0. This means that $\delta_{D} \in [0, \sqrt{d^{2} + 2\delta_{A}k_{D}}]$
\end{description}

\subsection{Best responses}
\subsubsection{$k_{D} > d$}
\begin{description}
\item if $\delta_{A} < 2(k_{D} - d)$ \\
For case 2.A it is increasing. 
\item $\delta_{A} = 2(k_{D} - d)$ \\
\item $\delta_{A} > 2(k_{D} - d)$ \\
In every case the function is decreasing so the defender will not play.
\end{description}

From this analyses we can compute $opt_{D}(\delta_{A})$ for two different cases as:
 \begin{displaymath}
  opt_{D}(\delta_{A}) = \left\{
     \begin{array}{lr}
       0, & \delta_{A} < 2(k_{D} - d)\\
       0, & \delta_{A} = 2(k_{D} - d) \\
       \big[0,\sqrt{d^{2} + 2\delta_{A}k_{D}}\big], & \delta_{A} > 2(k_{D} - d)
     \end{array}
   \right.
\end{displaymath}

For case :
 \begin{displaymath}
  opt_{D}(\delta_{A}) = \left\{
     \begin{array}{lr}
       0, & \delta_{A} < 2(k_{D} - d)\\
       0, & \delta_{A} = 2(k_{D} - d) \\
       \big[0,\sqrt{d^{2} + 2\delta_{A}k_{D}}\big], & \delta_{A} > 2(k_{D} - d)
     \end{array}
   \right.
\end{displaymath}
-------------------------------------------\\

\subsection{betaA}
We still consider the case where $d < \delta_{D}$. \\
To determine the Nash equilibria we also need to determine $opt_{1}(\delta_{D})$ by computing the derivative of $\beta_{A}(\delta_{D},\delta_{A})$ for a fixed $\delta_{D}$. We consider 2 cases: \\

\textbf{Case 1: $\delta_{A} \geq \delta_{D}$}\\

Since 
\begin{equation*}
\beta_{A}(\delta_{D},\delta_{A}) =\dfrac{\delta_{D}}{2\delta_{A}} - \dfrac{k_{A}}{\delta_{A}} + \dfrac{d^{2}}{2\delta_{D}\delta_{A}^{2}} - \dfrac{d}{\delta_{A}}
\end{equation*}
the derivative is:
\begin{equation*}
\dfrac{\partial \beta_{A}(\delta_{D},\delta_{A})}{\partial \delta_{A}} = -\dfrac{\delta_{D}}{2\delta_{A}^{2}} + \dfrac{k_{A}}{\delta_{A}^{2}} - \dfrac{d^{2}}{2\delta_{D}\delta_{A}^{2}} + \dfrac{d}{\delta_{A}^{2}}
\end{equation*}
it follows that $\beta_{A}(\delta_{D},\cdot)$ is increasing if $2k_{A} < (\delta_{D} - d)^{2} / \delta_{D}$ and decreasing if $2k_{A} > (\delta_{D} - d)^{2} / \delta_{D}$. \\

\textbf{Case 2: $\delta_{A} \leq \delta_{D}$ } \\

\textbf{A}: $\delta_{A} \leq d + \delta_{A} \leq \delta_{D}$ \\
Since 
\begin{equation*}
\beta_{A}(\delta_{D},\delta_{A}) =1- \dfrac{\delta_{A}}{2\delta_{D}} - \dfrac{k_{A}}{\delta_{A}} - \dfrac{d}{\delta_{D}}
\end{equation*}
the derivative is:
\begin{equation*}
\dfrac{\partial \beta_{A}(\delta_{D},\delta_{A})}{\partial \delta_{A}} = \dfrac{-1}{2\delta_{D}} + \dfrac{k_{A}}{\delta_{A}^{2}}
\end{equation*}
it follows that $\beta_{A}(\delta_{D},\cdot)$ is increasing on $[0,\sqrt{2k_{A}\delta_{D}}]$ and decreasing on $[\sqrt{2k_{A}\delta_{D}}, \infty]$ and thus has a maximum on $\delta_{A} = maximum \{\delta_{D}, \sqrt{2k_{A}\delta_{D}} \} $. The maximum between $\delta_{D}$ and $ \sqrt{2k_{A}\delta_{D}}$ is needed because $\delta_{A} $ cannot exceed $\delta_{D}$ in this case. \\

\textbf{B}: $\delta_{A}  \leq \delta_{D} \leq d + \delta_{A} $ \\

Since 
\begin{equation*}
\beta_{A}(\delta_{D},\delta_{A}) = 1 - \dfrac{\delta_{A}}{2\delta_{D}} - \dfrac{d}{\delta_{A}} - \dfrac{k_{A}}{\delta_{A}} + \dfrac{(d-(\delta_{D}-\delta_{A})^{2}}{2\delta_{D}\delta_{A}} 
\end{equation*}
the derivative is:
\begin{equation*}
\dfrac{\partial \beta_{A}(\delta_{D},\delta_{A})}{\partial \delta_{A}} = -\dfrac{\delta_{D}}{2\delta_{A}^{2}} + \dfrac{k_{A}}{\delta_{A}^{2}} - \dfrac{d^{2}}{2\delta_{D}\delta_{A}^{2}} + \dfrac{d}{\delta_{A}^{2}}
\end{equation*}
it follows that $\beta_{A}(\delta_{D},\cdot)$ is increasing if $2k_{A} < (\delta_{D} - d)^{2} / \delta_{D}$ and decreasing if $2k_{A} > (\delta_{D} - d)^{2} / \delta_{D}$. This is the same result as in case 1.\\
%%% Local Variables: 
%%% mode: latex
%%% TeX-master: "thesis"
%%% End:
